MSK IV

### 2017-07-24 msk4.rmd
updated path powpowpow

>>>>

# Path POW

## Arthritis

If the PIP extended and DIP flexed: swan neck deformity

| OA | RA | Both |
| ------------ | ----------- | ----------- |
| Minimal joint inflammation | Morning joint stiffness lasts >1 hour | Affects small joints of the hands |
| Joint pain worsens after use | Presence of extra-articular manifestations  | Visible nodules on hands |
| | Abnormal levels of autoantibodies  | | 
| | Mostly symmetrical polyarthritis affecting young females | |

Radiological

-  Both: loss of jt space, malalignment of joints
-  OA: subchondral cysts and sclerosis, formation of bony outgrowths at the end of joints
